Metagenomic Barcoding of Pollen Loads Offers Insights on the Foraging

### 2023-01-09 script/manuscript_MEE.Rmd
finally fixed header

---
title: Metagenomic Barcoding of Pollen Loads Offers Insights on the Foraging
  Patterns of Queen Bumble Bees
author: |  
  Reed Clark Benkendorf^[Correspondence: reedbenkendorf2021@u.northwestern.edu] $^1$$^,$$^2$, Jane E. Ogilvie $^3$, Emily J. Woodworth $^1$$^,$$^2$, Sophie Taddeo $^1$$^,$$^2$, Paul J. CaraDonna $^1$$^,$$^2$$^,$$^3$, Jeremie B. Fant $^1$$^,$$^2$ | $^1$Chicago Botanic Garden, 1000 Lake Cook Road, Glencoe, Illinois 60022 USA,  $^2$Plant Biology and Conservation, Northwestern University, Evanston, IL 60208, USA, $^3$ Rocky Mountain Biological Laboratory, P.O. Box 519, Crested Butte, CO 81224, USA]
abstract:  |
  1) DNA Barcoding has been remarkably successful in nearly all kingdoms of life and has allowed for the rapid analysis of ecological assemblages. Successful DNA barcoding in the plant kingdom has been more difficult than other kingdoms. Due to this understanding plants in ecological contexts and understandings of their synecology in some instances may begin to lag behind other kingdoms.  
  2) Here we utilize hyb-seq, museum studies, and species distribution modelling, to detect the plant species present in pollen loads collected from Queen Bumble Bees.  
  3) By utilizing Species distribution modelling we allow for one to process hyb-seq data, create user specified sequence databases which may use MORE ACCURATE alignment algorithms on personal computers over realistic time periods.  
  4) We show that hyb-seq using the Angiosperms 353 probes, which are currently being used in the largest ever plant systematic endeavor, offers significant promise to metagenomic approaches in real world scenarios.  
  5) We conclude that these probes offer promise for the identification of plant tissue in both single sample, and metasample contexts.  
#keywords: | 
#"DNA baroding, metagenomics, hyb-seq, Angiosperms353, plant metagenomics, bombus queens, subalpine, species #distribution model"
output:
  pdf_document: default
  toc: no
  pandoc_args:
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
  word_document: default
csl: "../citations/methods-in-ecology-and-evolution.csl"
bibliography: ../citations/citations.bib
link-citations: yes
fig_caption: yes
always_allow_html: true
header-includes:
- \usepackage{endfloat}
- \usepackage{setspace}\doublespacing
- \usepackage{lineno}
- \linenumbers
---

>>>>

---
title: Metagenomic Barcoding of Pollen Loads Offers Insights on the Foraging
  Patterns of Queen Bumble Bees
author:  |
    |  Sophie Taddeo $^1$$^,$$^2$, Paul J. CaraDonna $^1$$^,$$^2$$^,$$^3$, Jeremie B. Fant $^1$$^,$$^2$ 
    |  $^1$Chicago Botanic Garden, 1000 Lake Cook Road, Glencoe, Illinois 60022 USA, 
    |  $^2$Plant Biology and Conservation, Northwestern University, Evanston, IL 60208, USA,
    |  $^3$Rocky Mountain Biological Laboratory, P.O. Box 519, Crested Butte, CO 81224, USA
    |  Reed Clark Benkendorf^[Correspondence: reedbenkendorf2021@u.northwestern.edu] $^1$$^,$$^2$, Jane E. Ogilvie $^3$, Emily J. Woodworth $^1$$^,$$^2$  
abstract:  |  
  1) DNA Barcoding has been remarkably successful in nearly all kingdoms of life and has allowed for the rapid analysis of ecological assemblages. Successful DNA barcoding in the plant kingdom has been more difficult than other kingdoms. Due to this understanding plants in ecological contexts and understandings of their synecology in some instances may begin to lag behind other kingdoms.  
  2) Here we utilize hyb-seq, museum studies, and species distribution modelling, to detect the plant species present in pollen loads collected from Queen Bumble Bees.  
  3) By utilizing Species distribution modelling we allow for one to process hyb-seq data, create user specified sequence databases which may use MORE ACCURATE alignment algorithms on personal computers over realistic time periods.  
  4) We show that hyb-seq using the Angiosperms 353 probes, which are currently being used in the largest ever plant systematic endeavor, offers significant promise to metagenomic approaches in real world scenarios.  
  5) We conclude that these probes offer promise for the identification of plant tissue in both single sample, and metasample contexts.  
keywords: |  
  DNA baroding, metagenomics, hyb-seq, Angiosperms353, plant metagenomics, bombus queens, subalpine, species distribution model
output:
  word_document: default
  toc: no
  pandoc_args:
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
  pdf_document: default
csl: "../citations/methods-in-ecology-and-evolution.csl"
bibliography: ../citations/citations.bib
link-citations: yes
fig_caption: yes
always_allow_html: true
header-includes:
- \usepackage{endfloat}
- \usepackage{setspace}\doublespacing
- \usepackage{lineno}
- \linenumbers
---
